This module is the inverse Fast Level Sets Transform (see module flst). From
the tree of shapes of an image, it builds back the image. If the tree was not
modified since the call to the module flst, the reconstruction gives of course
the initial image. So that interesting reconstructions happen when something
has changed in the graph, for example gray levels were changed, or some shapes
were removed.

The reconstruction algorithm is elementary: for each pixel, we know the
smallest shape containing it (given by the function
\texttt{mw\_get\_smallest\_shape}) and we put at this pixel the gray level value
of the shape.

If the root of the tree was not removed (this operation is forbidden), any
other manipulation of the tree is allowed, but:
\begin{itemize}
\item if the gray level of one shape is changed, its relation to the gray
level of its father and to the gray levels of its children must be preserved;
that means that the order of these gray levels must remain the same.
\item if a shape is removed, the order of the gray levels between its parent
and its children must remain the same.
\end{itemize}
If these conditions are fulfilled, then it is guaranteed that the tree is
consistent with the image it represents. That means that reconstructing the
image from such a tree and then decomposing again the result with the flst
module, we get the same tree. Such modifications of the tree are called
allowable modification.

For example, removing a leaf of the tree is an allowable modification. Also,
removing a shape of the same type as its father and as its children is
allowable.
