This module is designed to allow an interactive visualization of curves.
\index{visualization!of a curve}
The requested input is a Flists structure, but thanks to
MegaWave2 automatic format conversions, all kinds of curves 
(Fcurve, Curve, Curves, Polygon, Flist, Dlist(s), \ldots) can be 
used as input in a shell call. The visualization window has a default
size of $800\times 600$, but it can be changed using the \verb+-x+ and
\verb+-y+ options. A background image (\verb+-b+ option)
can also be specified (this may
be useful when the curves to visualize are related to the geometry of this
image for example). 

\medskip

Unless the \verb+-a+ option is used, the $x/y$ ratio is preserved between
the region displayed and its corresponding part on the screen.
If the \verb+-a+ option is specified, the zoom factor may differ in the
$x$ and in the $y$ direction, yielding an affine scaling. 
The \verb+-s+ option places origin in the downleft corner of the window
(instead of upleft). The display style is set by the \verb+-d+ option~:
the curves can be drawn as isolated points ($d=1$), as lines ($d=2$, 
the default) or as lines plus points ($d=3$). The endpoints of the curves
can also be marked using the \verb+-e+ option. 
A particular curve can be selected with the mouse left button. 
It will appear in red. The 'a' and PageUp/Down keys allow to 
view the curves separately. With the 'm' key, curve evolutions can
be easily visualized.

\medskip

A reference curve can be used to set the display window (it is useful to
visualize at the same scale the successive evolutions of a given curve). 
If the \verb+-C+ option is specified, this reference curve will be
displayed in the specified color (3 decimal digits RGB color: 
0 is black, 999 is white, 900 is full red, etc.).

\medskip

The \verb+-o+ option allows
to save the last visualized image as a Ccimage; it can be combined with
the \verb+-n+ option (that prevents the display) to bitmap the curves
in a Cimage.

\medskip

{\bf Interactive commands~:}
\medskip

\begin{tabular}{ll}
Key 'q'			& quit \\
Key 'h'			& help \\
Key 'a'			& toggle all/single display \\
Key 'b'			& toggle background image \\
Key 'c'			& toggle current curve display \\
Key 'e'			& toggle extremal points (\verb+-e+ option) \\
Key 'g'			& switch grid mode (\verb+-g+ option) \\
Key 'k'			& change current curve index \\
Key 'm'			& toggle motion \\
Key 'n'			& toggle curve index display \\
Key 'p'			& toggle display style (\verb+-d+ option)\\
Key 's'			& symmetrize y axis (\verb+-s+ option)\\
Key 'u'			& unzoom $\times 2$ \\
Left Arrow		& go Left\\
Right Arrow		& go Right\\
Up Arrow		& go Up\\
Down Arrow		& go Down\\
Page Up      		& previous curve.\\
Page Down    		& next curve.\\
\\
Mouse Left button 	& select a curve \\
Mouse Middle button 	& restore the original display region \\
Mouse Right button	& zoom $\times 2$, centered at mouse origin \\
\end{tabular}
