%
% Part 8 of the MegaWave2 Guide #2
%   Raw data
%

When none of the previous structures matches your need, or when you want to
write or to read files in a format which is not recognized by MegaWave2, use
the raw data\index{raw data} type : this internal type allows you to load/save 
any kind of data from/to disk.

%+++++++++++++++++++++++++++++++++++++++++++++++
\section{The structure Rawdata}
%+++++++++++++++++++++++++++++++++++++++++++++++

\def\rawdata{{\tt Rawdata}}
\index{structure!\rawdata}
\label{rawdata_structure}

The \rawdata\ structure is nothing else than an array of bytes (\verb+data+ field). The
size of the array is set in the \verb+size+ field.

{\small
\begin{verbatim}
typedef struct rawdata {
  int size;               /* Number of samples */
  unsigned char *data;    /* data field */
} *Rawdata;
\end{verbatim}
}

%+++++++++++++++++++++++++++++++++++++++++++++++
\section{Related file (external) types}
%+++++++++++++++++++++++++++++++++++++++++++++++
\label{rawdata-file_type}

There is no file types associated to the \rawdata\ structure : when the content of a \rawdata\ 
variable is written into a file, the content of the file is exactly the content of the \verb+data+
field. There is no header added. Consequently, file of any format can be loaded into a \rawdata\
variable. If this file contains a header (as most of MegaWave2 file formats), the header will
be loaded into the \verb+data+ field together with the data themselves.
Of course, there cannot be any conversion format associated to \rawdata.

%+++++++++++++++++++++++++++++++++++++++++++++++
\section{Functions Summary}
%+++++++++++++++++++++++++++++++++++++++++++++++
\label{rawdata_function}

The following is a description of all the functions related to 
the \rawdata\ type. The list is in alphabetical order.

\newpage %......................................

\input{chapter_08_rawdata.tex}
