\def\vfp{\vspace{5mm}}
\def\la{_\lambda }
\def\ut& {\frac{\partial u}{\partial t}}
\def\equi& {\Leftrightarrow}
\def\fb& {\begin{equation}}
\def\fe& {\end{equation}}
\def\med{\hbox{med}}
\def\real{I\!\!R}
\def\entier{I\!\!N}
\def\MONO {{\tt [Order Preserving] }}
\def\Morp {{\tt [Morphology] }}
\def\MORP {{\tt [Pure Morphology] }}
\def\CONS {{\tt [Consistency] }}
\def\CONV {{\tt [Convergence] }}
\def\ECHE {{\tt [Scale invariance] }}
\def\ROTA {{\tt [Isom. invariance] }}
\def\AFFI {{\tt [Affine invariance] }}
\def\skipaline {\vspace{4 mm}}

{\center {\bf \underbar{ Multiscale Analysis of image.}}}

The fundamental equation of image processing
\fb&
\hbox{AMSS} \qquad \frac{\partial u}{\partial t} = \vert Du \vert (curv(u))^{\frac{1}{3}} 
\fe&
$$ u(0,.) = u_0(.)$$
has been discovered recently with existence proofs in the sense of viscosity
solutions [AGLM-1-2-3]. 
This is the unique model of multiscale analysis of image, affine invariant and morphological
invariant.

Another useful, less invariant (not affine invariant), but more easy for a numerical viewpoint,
is the same equation without the power $1/3$ : ``the mean curvature motion".

\fb&
\hbox{MCM} \qquad
\frac{\partial u}{\partial t} = \vert Du \vert (curv(u)) 
\fe&


The function {\bf amss} will process the model AMSS or the mean curvature motion, from $t = t_{begin}$ to $t = t_{end}$.


\skipaline
{\bf INPUTS of amss.}


\begin{description}

\item[ image] \ = {\bf u } is the original picture (type : fimage).

\item[- p] 

By default, the module process the mean curvature motion (MCM). 
By selecting this option, the module process the AMSS model.

\item[- l] \ lastScale =LS \\
{\bf amss} will process the equation (1) or (2) until the normalised scale equals LS.

The normalised scale is defined such
 that a circle of radius LS in the original image, 
disapears when the normalised scale = LS.
Then the rescaling depends of the power of the curvature :

If MCM (equation(2)), then $t_{end} = $ LS$^2 / 2$.

If AMSS (equation(1)), then $t_{end} = $ LS$^\frac{4}{3} \times 3 /4$.

If this option is not used LS$=2.0$.

\item[- f] \ firstScale = FS \\
This option allows to fix $t_{begin}$ non equal to zero. Suppose that, for example,
we have already calculated the image $u$ at scale 2: $u_2$, and we want to have 
it at scale 4: $u_4$.
We can apply {\bf amss} to $u_2$. But, we must precise to {\bf amss} that $u_2$ 
is already at scale 2, by using option
-f 2. Then, the instruction : amss -f 2 -t 4 $u_2$ will process $u_4$.

As for LS, FS is a normalized scale.

If this option is not used, FS is 0.

\item[ -s] \ OutPutStep \\

OutPutStep is the scale interval between two diffusions (default is $0.1$):
the module will process the image at each normalised scale : 
k $\times$ OutPutScale + FS, until LS (k $\in \entier$).

\item[ -S] \ Step \\
 Step is the interval of scale for the discretization of the equations.
$$\frac{\partial u}{\partial t} = \frac{u(.,t+step) - u(.,t)}{step} $$
It must be a float number and nonnegative (default value is $0.1$).

For AMSS model Step must be lower than 0.1, for the mean curvature motion Step must 
be lower than 0.5. Then, \par

If MCM,  then Step must be $\leq$ 0.1. 

If AMSS,  then Step must be $\leq$ 0.5.


The number of iterations needed by {\bf amss} is calculated as following :
If MCM
$$ \hbox{Number of iterations} = \frac{LS^2 - FS^2}{2*Step}$$

If AMSS
$$ \hbox{Number of iterations} =  \frac{3}{4}\frac{ LS^\frac{4}{3} - FS^\frac{4}{3}}{Step}
$$

\item[ -i]

By default, the module will process an isotropic diffusion 
when the estimated gradient is less than {\it MinGrad}. 
This can be useful to avoid a problem of our discretization :
suppose the image is a black point on white background, then our estimated
gradient by centered finite differences is equal to zero at this point. 
Then, it never disappears.

The \verb+-i+ flag cancels this isotropic diffusion : 
nothing will be done at points with gradient norm less than {\it MinGrad}.



\end{description}


{\bf OUTPUTS of amss.}

Several outputs can be selected among diffusion image, gradient and curvature,
 in the Fimage type (for last scale) or Cmovie type 
(for all intermediate scales). Notice that for Cmovie type, precision
may be lost since a conversion from floating point values to char 
values is necessary. For the curvature, a normalization $k\mapsto 100k+128$
is performed, but it can be cancelled using the \verb+-n+ option.

\vskip 3cm

{\bf \Large Numerical scheme.}

Equations (1) and (2) verify the following properties 
\begin{itemize}
\item \MONO, because they both are parabolic equations.
\item \Morp, the analysis commute with a monotonous rescaling of the grey level scale.
\item \ECHE, the analysis commute with zoom.
\item \ROTA, the analysis commute with isometry.
\item \AFFI, for only the equation (1) AMSS model.
\end{itemize}

The scheme is based on a diffusive interpretation of the equations.
Indeed, if $\xi$ is a unit vector, such that $\nabla u . \xi = 0$,
and $u_{\xi\xi}$ the second derivative of u in the direction $\xi$,
we have :
$$ (2) \equi& \ut& = u_{\xi\xi} $$
This formulation yields an anisotropic diffusion equation. Anisotropic,
because we diffuse only in one direction $\xi$, depending on the gradient.
(compare with the isotropic diffusion ($\ut& = \Delta u$) i.e. the
heat equation).

Equation (1) can be rewritten as
$ \ut& = ( \nabla u )^{\frac{2}{3}} (u_{\xi\xi})^{\frac{1}{3}} $,
where $( \nabla u )^{\frac{2}{3}}$ is understood as the speed of the diffusion.


The schemes which we wish to discuss compute $u_{\xi\xi}$ by a quasilinear formula in the sense defined above.

\skipaline
In order to have consistency, we must find $\lambda_0 , \lambda_1 , \lambda_2 ,
\lambda_3, \lambda_4$, such that :
\fb& \label{KKK}
u_{\xi\xi} = \frac{1}{\Delta x^2} ( -4 \lambda_0 u_{i,j} + \lambda_1 (u_{i+1,j}
+u_{i-1,j}) + \lambda_2 (u_{i,j+1} +u_{i,j-1})
\fe&
$$
    \qquad + \lambda_3 (u_{i-1,j-1} +u_{i+1,j+1}) +\lambda_4 (u_{i-1,j+1} +u_{i+
1,j-1}))
+o(1)
$$

\CONS implies

$$
\begin{array}{l}
 \lambda_1(\theta) = 2 \lambda_0(\theta) - \sin^2\theta \\
 \lambda_2(\theta) = 2 \lambda_0(\theta) - \cos^2\theta \\
 \lambda_3(\theta) = - \lambda_0(\theta) + 0.5(\sin \theta \cos \theta + 1) \\
 \lambda_4(\theta) = - \lambda_0(\theta) + 0.5(-\sin \theta \cos \theta + 1) 
 \end{array}
$$
We choose for several reasons (see [CEGLM]):
$$ \lambda_0(\theta) = 0.5 - \cos^2(\theta) +\cos^4(\theta) $$

We deduce the others $\lambda$'s:

$$
\left\{
\begin{array}{l}
-4 \lambda_0 = -2 + 4 \cos^2(\theta)\sin^2(\theta) \\
\lambda_1 = \cos^2(\theta) (\cos^2(\theta) - \sin^2(\theta)) \\
\lambda_2 = \sin^2(\theta) (\sin^2(\theta) - \cos^2(\theta)) \\
\lambda_3 = \cos^2(\theta)\sin^2(\theta) + 0.5 \sin(\theta)\cos(\theta) \\
\lambda_4 = \cos^2(\theta)\sin^2(\theta) - 0.5 \sin(\theta)\cos(\theta) \\
\end{array}
\right.
$$


Then our estimation of $u_{\xi\xi}$, is exact for all the linear combinations of the polynom
ials
 of degree 0,1,2 and 3, plus the polynomial :$(x^2+y^2)(x \sin\theta - y \cos\theta ) ^2$. 
Of course, the calculus can be false for the other polynomials.

{\bf algorithm.}


  Our algorithm is following:


\begin {itemize}

\item We estimate the gradient direction $\theta$, and $\xi$ the orthogonal direction
using the 9 points of the stencil 3x3.

\item Computation of $curv(u)$ as above.

\item We proceed, in case of equation

\end {itemize}

$$ \begin{array}{l} \hbox{(2) : } \qquad u^{n+1}(x) = u^{n}(x) + \Delta t u^n_{\xi\xi}(x)
\\ \hbox{(1) : } \qquad u^{n+1}(x) =u^{n}(x) +
 \Delta t (Du)^{2/3} (u^n_{\xi\xi}(x))^{1/3} \end{array} $$

In the case of (2) i.e. mean curvature motion, we must choose $\Delta t \leq 0.5 (\Delta x)^2$
 in order to have some stability.
Whereas for (1) i.e. AMSS model , the maximum value of $\Delta t$ cannot be imposed
theoretically.


This scheme verifies \CONS, because it is exact at order 2.
All the geometrical properties (\ROTA, \ECHE, ...) are true for
all the polynomials mentionned above. For other functions, we have these properties only
 for the affine transforms which leave the grid invariant.

\underbar{But, the scheme is not morphological.}
And, it does not satisfy \MONO. However, it is experimentally
quite stable.
In fact, we do not expect to have \MONO and \CONS in such a quasilinear scheme
with a fixed stencil. If you impose both, as noticed in [ALM] and proved 
by [CrLi], you do not limit the size of the stencil.
 
