\def\Om{\Omega}
\def\la{\lambda}
\def\gu{\nabla u}
\def\ve{\varepsilon}
\def\lp#1{{L}^{#1}}
\def\wlp#1#2{{W}^{#1,#2}}
\def\HunO{{H}^1(\Om)}
\def\ltwo{\lp{2}}
\def\ltwoO{\ltwo(\Om)}
\def\ds{\displaystyle}
\def\Ref#1{(\ref{#1})}

This module applies the Total Variation Minimization algorithm described
below to a color image \verb+in+, during the time $\delta t$ given by
\verb+deltat+.
The result is a diffused (smoothed) color image put in \verb+out+ which 
keeps the sharpness of the edges.
Such algorithm may be used to restore a noisy image.

To get a sequence of diffused images, see the module \verb+cfmdiffuse+.

\medskip

The following is a short description of the used scheme, the Total Variation Minimization via a Relaxation Algorithm.
For more information please see \cite{ChambolleLions}.

Let $\Phi_\ve$ be the following $C^1$ function:
\begin{equation}\label{defphi}
\Phi_\ve : x \mapsto \left\{ \begin{array}{ll}
\ds{{1\over 2\ve} x^2} & \mbox{if } |x|\leq \ve \\
\ds{|x|-{\ve\over 2}}  & \mbox{if } \ve \leq |x| \leq \ds{1\over \ve} \\
\ds{{\ve\over 2} x^2 + {1\over 2}({1\over \ve}-\ve)}
& \mbox{if } |x|\geq \ds{1\over \ve}
\end{array}\right.
\end{equation}
and consider the problem
\begin{equation}\label{PLMap}
\mbox{Minimize } \int_\Om \Phi_\ve(|\gu|) + \frac{\la}{2} |u-u_0|^2
\end{equation}
where $u\in \HunO = \wlp{1}{2}(\Om)$.

As $\ve$ goes to zero it may be shown that the minimizer of~\Ref{PLMap}
goes to the minimizer of the following energy:
\begin{equation}\label{PLMap2}
\int_\Om |\gu| + \frac{\la}{2} |u-u_0|^2.
\end{equation}

Now, set for simplicity's sake
$\la = 1$ and choose a small, fixed $\ve$ (for instance, 1).
In the sequel we will denote $\Phi_\ve$ simply by $\Phi$.
Consider the following functional:
\begin{equation} \label{erelax}
E(u,v) = \int_\Om v |\gu|^2 + {1\over v} + |u-u_0|^2
\end{equation}
where $u\in \HunO$ and $v\in \ltwoO$, $\ve \leq v \leq 1/\ve$.

Start from any $u^1$ and $v^1$ (for instance $v^1\equiv 1$) and
let:
\begin{equation}
\begin{array}{rcccl}
u^{n+1} &=& \ds{\mbox{arg}\min_{u\in \HunO} E(u,v^n)} & & \\
v^{n+1} &=& \ds{\mbox{arg}\min_{\ve \leq v \leq 1/\ve} E(u^{n+1},v)} &=&
\ds{ \ve \vee {1\over |\gu^{n+1}|} \wedge {1\over \ve}}
\end{array}\end{equation}
($u^{n+1}$ is therefore characterized by
\[ \forall \phi\in \HunO, \int_\Om v^n\gu^{n+1}\cdot\nabla \phi
+ (u^{n+1}-u_0) \phi = 0, \]
{\em i.e.\/} $-\mbox{div}(v^n\gu^{n+1}) + u^{n+1} = u_0$ in ${\HunO}'$.)

We have the following result.
\medskip

%\begin{proposition}
{\sc Proposition. }
{\em The sequence $(u_n)$
converges (strongly in $\ltwoO$ and weakly in $\HunO$)
to the minimizer of~\Ref{PLMap}.}
%\end{proposition}
\medskip

Now, to solve the PDE
\[ \frac{\partial u}{\partial t} = \mbox{div} \frac{\gu}{|\gu|} \]
or, to be more precise,
\[ \frac{\partial u}{\partial t} = \mbox{div} \frac{\Phi{\gu}}{|\gu|}\gu \]
we simply compute $u(t+\delta t)$ by minimizing~\Ref{PLMap} with
$u_0 = u(t)$ and $\lambda = 1/\delta t$.

\begin{thebibliography}{99}
\bibitem{ChambolleLions}
A.~Chambolle and P.-L. Lions.
\newblock Image recovery via total variation minimization and related problems.
\newblock Preprint, 1995.
\end{thebibliography}
