This module is designed to allow an interactive visualization of curves.
The requested input is a Fcurves structure, but thanks to
MegaWave2 automatic format conversions, all kinds of curves 
(Fcurve, Curve, Curves, Polygon, etc\ldots) can be 
used as input in a shell call. The visualization window has a default
size of $800\times 600$, but it can be changed using the \verb+-x+ and
\verb+-y+ options. A background image (\verb+-b+ option)
can also be specified (this may
be useful when the curves to visualize are related to the geometry of this
image for example). In this case, the window size is set by the
background image. A translation and zoom is then performed in order that
the Fcurves size fits at least one of the window dimensions. 
If the \verb+-a+ option is specified, the zoom factor may differ in the
$x$ and in the $y$ direction, yielding an affine scaling. 
The \verb+-s+ option places origin in the downleft corner of the window
(instead of upleft). The display style is set by the \verb+-d+ option~:
the curves can be drawn as isolated points ($d=1$), as lines ($d=2$, 
the default) or as lines plus points ($d=3$). The endpoints of the curves
can also be marked using the \verb+-e+ option. The \verb+-o+ option allows
to save the last visualized image as a Cimageé; it can be combined with
the \verb+-n+ option (that prevents the display) to bitmap a Fcurves
in a Cimage.

\medskip

{\bf Interactive commands~:}
\medskip

\begin{tabular}{ll}
Key 'q'			& quit \\
Key 'h'			& help \\
Key 'u'			& unzoom $\times 2$ \\
Key 's'			& symmetrize along y coordinate (\verb+-s+ option)\\
Key 'p'			& toggle display style (\verb+-d+ option)\\
Key 'e'			& toggle extremal points (\verb+-e+ option) \\
Mouse Left button 	& center the window at mouse origin \\
Mouse Middle button 	& restore original settings \\
Mouse Right button	& zoom $\times 2$, centered at mouse origin \\
\end{tabular}
