
This module performs an affine normalization or/and a thresholding
on the image $in$, according to the selected options.

\medskip

If neither the \verb+-n+ nor the \verb+-N+ option is selected,
then a simple thresholding is performed, constraining the 
minimum and/or maximum value of the grey-level to stay
inside specified bounds with the \verb+-m+ and \verb+-M+ options.

\medskip

If the \verb+-n+ option is selected, then an affine normalization
is performed to send the interval $[m,M]$ onto the interval $[min,max]$,
where $m$ and $M$ are minimal and maximal values of the input image
$in$ (default), or selected percentiles of its histogram if the \verb+-p+,
\verb+-q+ or \verb+-d+ options are used. In the latter case, a thresholding
is then applied unless the \verb+-a+ option is selected.

\medskip

If the \verb+-N+ option is selected, then an affine normalization
is performed to send the interval $[m,M]$ onto the interval $[0,255]$,
where $m$ and $M$ are minimal and maximal values of the input image
$in$ (default), or selected percentiles of its histogram if the \verb+-p+,
\verb+-q+ or \verb+-d+ options are used, or fixed values if the \verb+-m+
and \verb+-M+ options are used. Like for the \verb+-n+ option, thresholding
can be avoided by using the \verb+-a+ option.

\medskip

In all cases, a linear (instead of affine) normalization can be enforced
by selecting the \verb+-l+ option. In this case, minimum values are not
used for normalization (but they are used for thresholding).
