\def\real{I\!\!R}


{\em iowave2} reconstructs an image from a sequence of sub-images forming 
a wavelet decomposition, according to the pyramidal algorithm of S. Mallat 
\cite{kn:ma1}. 
The notations that are used here have been already defined in {\em owave1} 
and {\em owave2} modules' documentation, so the reader is refered 
there to see their signification. 

{\em WavTrans} is the prefix name of a sequence of files containing 
the coefficients of a wavelet decomposition  $D^{1}_{1}, D^{1}_{2}, \ldots, 
D^{1}_{J}, D^{2}_{1}, \ldots D^{2}_{J}, D^{3}_{1}, \ldots, D^{3}_{J}, A_{J}$. 
{\em iowave2} computes \( A_{0} \), i.e. the inverse wavelet transform 
of {\em WavTrans}. 

As for {\em owave2} this is a semi-separable and recursive transformation : 
\( A_{j-1} \) is computed from \( A_{j} \) \( D^{1}_{j} \), \( D^{2}_{j} \), 
and \( D^{3}_{j} \). One applies the one-dimensional inverse wavelet transform 
to each pair of corresponding lines in \( A_{j} \) and \( D^{1}_{j} \) and in 
$D^{2}_{j}$, and $D^{3}_{j}$. Then one applies the one-dimensional inverse 
wavelet transform to each pair of corresponding columns in the two resulting 
sub-images. 

The edge processing methods are corresponding to those described for 
{\em iowave1}.

The complexity of the algorithm is roughly the same as for {\em owave2}.

The name of the files containing the sub-signals 
$D^{1}_{1}, D^{1}_{2}, \ldots, D^{1}_{J}, D^{2}_{1}, \ldots D^{2}_{J}, 
D^{3}_{1}, \ldots, D^{3}_{J}, A_{J}$ must have the same prefix {\em WavTrans}, 
and their syntax obeys the rules described in {\em owave2}. 
The sample values of the reconstructed signal are stored in the file 
{\em RecompImage}. 

The coefficients \( h_{k} \) of the filter's impulse response are read 
in the file {\em ImpulseResponse}. The coefficients of the filter's 
impulse response for computing the edge coefficients are read in the file 
{\em EdgeIR}. 


\begin{itemize}
\item
The -r option specifies that the reconstruction should start from level 
{\em NLevel}. The default is the number of level in {\em WavTrans}. 
\item
The -h option specifies that the reconstruction should start from level 
{\em HaarNLevel} up to level {\em NLevel + 1} with the Haar filter. 
\item
The -e option specifies the edge processing mode (see {\em owave1}).
\item
The -p option specifies the preconditionning mode (see {\em iowave1}).
\item
The -i option enables to have invertible transform. Since the transform is invertible when EdgeMode is equal to 1 or 3, this only makes sense when EdgeMode is equal to 0 or 2. 
\item
The -n option specifies the normalisation mode of the filter impulse responses' coefficients. It should be selected according to the mode used for the decomposition in order to get exact reconstruction. 
\end{itemize}

These options should be tuned in the same way as they were 
for the decomposition (with the {\em owave2} module). 

\begin{thebibliography}{Dau1}

\bibitem[CDV]{kn:cdv} A. Cohen, I. Daubechies, P. Vial. 
{\em Wavelets and Fast Wavelet Transform on an Interval, } 
preprint AT\&T Bell Laboratories, 1992.
\bibitem[Dau]{kn:dau1} I. Daubechies. 
{\em Orthonomal Bases of Compactly Supported Wavelets, } 
Comm. pure and applied math., 41, pp.909--996, 1988.
\bibitem[Mal]{kn:ma1} S. Mallat. {\em a theory for multiresolution signal decomposition, the wavelet representation, } IEEE PAMI Vol. 2, n 7, 1989.

\end{thebibliography}

