The first task perfomed by this module is to determine which pairs of
normalized codes from \verb+dict1+ and \verb+dict2+ are good
candidates to match. This is done by calling the
\verb?km_prematchings? module : for every similitude-invariant 
code in \verb+dict1+, this module gets its pre-matching codes in
\verb+dict2+. The maximum Hausdorff distance between normalized codes
allowed here is \verb+maxError1+. Notice that the purpose of the
pre-matching step is to discard matchings that are clearly bad, in
order to reduce computational burden (since the extension step is much
more heavy). That's why the \verb+maxError1+ threshold should not be
too much restrictive; \verb+maxError1+ = 0.2 or 0.3 is a reasonable
choice.

Then matching extension is performed for all pre-matchings. For every
pair $({\mathcal S}_1,{\mathcal S}_2)$ of ``pre-matched'' pieces of
curve (sub-curves of ${\mathcal C}_1$ and ${\mathcal C}_2$, resp.),
the euclidean transformation that maps ${\mathcal S}_1$'s local frame
to ${\mathcal S}_2$'s local frame is computed. Then, this
transformation is used to put ${\mathcal C}_1$ and ${\mathcal C}_2$ in
the frame of image 2. In this frame, lengths and distances between
curves are measured in pixels. The matching extension step is based on
the following parameters: \verb+maxError2+, \verb+minLength+ and
\verb+minComplex+.

\begin{itemize}
  
\item \verb+maxError2+ controls the euclidean pixel distance between
  corresponding points of both curves (extracted by regular sampling
  in their normalized frames). 
  
\item \verb+minLength+ controls the minimum arc length required to
  both matched pieces of curve (in their original image frames) to be
  considered as a valid matching pair. In other words, initial pieces of
  curve are extended until their distance exceeds \verb+maxError2+; if
  their arc length is less than \verb+minLength+, the matching pair is not
  considered as a valid one.
  
\item Matching pieces of curve whose arc length is greater than
  \verb+minLength+ are considered to be valid if their total angle
  variation is greater than \verb+minComplex+.

\end{itemize}

For every piece of curve in image 1 we keep, among all possible valid
matching pieces, the one which maximizes the following criterion:

$$\mbox{Performance} = \frac{l_1 \times l_2}{L_1 \times L_2},$$

where $l_1=arclength(S_1)$, $l_2=arclength(S_2)$, $L_1=arclength(C_1)$
and $L_2=arclength(C_2)$.

Finally, the result is written in two different formats in Flists
\verb+matching+ and \verb+matching_pieces+. 

\begin{itemize}

\item \verb+matching+ is a 2 dimensional Flist that contains all pairs
$(i_1,i_2)$, where $i_1$ is the index of the original normalized code
in dictionary \verb+dict1+ and $i_2$ is the index of the original
normalized code in dictionary \verb+dict2+.

\item \verb+matching_pieces+ is a 7 dimensional Flist containing the
  following information:

  \begin{itemize}

  \item {\em First and second elements}: indices $NCurve1$ and
    $NCurve2$, which identify curves ${\mathcal C}_1$ and ${\mathcal C}_2$
    in Flists \verb+levlines1+ and \verb+levlines2+, resp.
  
  \item {\em Thirth and fourth elements}: first and last indices of the
    matching piece, in curve $NCurve1$.

  \item {\em Fifth and sixth elements}: first and last indices of the
    matching piece, in curve $NCurve2$.

  \item {\em Seventh element}: performance.
    
  \end{itemize}

\end{itemize}

This last output is to be used with the MegaWave2
module \verb+km_savematchings+. The
outputs of \verb+km_savematchings+ are two Flists that contain all pieces of
curve in image 1 and image 2 that match; they can be displayed using
\verb+fkview+.

\bigskip
See \cite{joseluis} or \cite{LMMM} for further details.


\begin{thebibliography}{9}

\bibitem{joseluis} J.-L. {\sc Lisani}, {\it Comparaison automatique
d'images par leurs formes}, th\`ese de doctorat, Universit\'e Paris IX
Dauphine, France, 2001.

\bibitem{LMMM} J.-L. Lisani, P. Monasse, L. Moisan, J.-M. Morel, 
``On the Theory of Planar Shape'', 
{\it SIAM Journal on Multiscale Modeling and Simulation}, 
vol. 1:1, pp. 1-24, 2003. 

\end{thebibliography}

