This module is mainly an auxiliary module for
\verb+km_match_si+ and \verb+km_match_ai+. It
computes all pairs of curves that are good candidates to match
(pre-matchings). However, it can be used independently from
these modules.

\verb+dict1+ and \verb+dict2+ contain $N_1$ and $N_2$ normalized codes
of pieces of curves of images 1 and 2. To be more precise,
\verb+dict1+ $=\{{\mathcal C}^1_i, 0 \leq i \leq N_1-1 \}$ and
\verb+dict2+ $=\{{\mathcal C}^2_j, 0 \leq j \leq N_2-1 \}$.  Both
dictionaries must have been computed using the same MegaWave module
(\verb+km_createdict_si+ or \verb+km_createdict_ai+).

\verb+km_prematchings+ returns an \verb+Flists+ that containts $N_1$
\verb+Flist+. The $i$-th \verb+Flist+ contains the indices $j$ of all
the codes of \verb+dict2+ that satisfy $d_H({\mathcal C}^1_i,{\mathcal
  C}^2_j) < $ \verb+maxError+, where $d_H$ is the Hausdorff distance. 

It should be noted that \verb+maxError+ is a distance between
normalized codes and not a distance between curves in the image frame,
and typically its value is to be chosen in the range $[0.1,0.3]$.

\bigskip
See \cite{joseluis} or \cite{LMMM} for further details.


\begin{thebibliography}{9}

\bibitem{joseluis} J.-L. {\sc Lisani}, {\it Comparaison automatique
d'images par leurs formes}, th\`ese de doctorat, Universit\'e Paris IX
Dauphine, France, 2001.

\bibitem{LMMM} J.-L. Lisani, P. Monasse, L. Moisan, J.-M. Morel, 
``On the Theory of Planar Shape'', 
{\it SIAM Journal on Multiscale Modeling and Simulation}, 
vol. 1:1, pp. 1-24, 2003. 

\end{thebibliography}
