Let us denote the data of the {\tt fsignal} {\em levels} ({\bf -l} option) by
$v_0, v_1,\ldots, v_N$, e.g. {\em levels-$>$size}$=N+1$\,. \\
For the {\bf -L} option we have $N=0$\,.

\smallskip

Moreover we recall that a {\tt morpho\_line} is the boundary of the set
$$ MS=\{(i,j) \;/\; \mbox{\em minvalue}\leq 
                       g(i,j)\leq\mbox{\em maxvalue} \}$$
where $g$ is the original picture {\em image\_in}. The {\em minvalue} and
the {\em maxvalue} define the ``thickness'' of the slice which is cut
 through the graph of {\em image\_in}. The set $MS$ is made out of 
connected sets and its boundary is composed of closed curves and of
open curves (which necessarily go from one border of the image to another).
Notice that the inequalities which define $MS$ are not strict.

\smallskip

The module {\bf ml\_extract} computes 
the {\tt morpho\_lines} of {\em image\_in}
where the {\em minvalue} and {\em maxvalue} are defined 
through the choice of option {\bf -o}.  \\
The different possibilities for {\em ml\_opt} are\,:
\begin{itemize}
\item[ 0 ] Here {\em minvalue}=$v_i$ and 
  {\em maxvalue}=$+\infty$\,, this gives the boundary of level sets \\
such that $v_i\leq g(i,j)$\,.
This is the default. 
\item[ 1 ] With this option  {\em minvalue}=$-\infty$ and 
  {\em maxvalue}=$v_i$\,, which gives the boundary of level sets 
such that $g(i,j)\leq v_i$\,.
\item[ 2 ] This option allows to compute isolines, thus 
 {\em minvalue}={\em maxvalue}=$v_i$\, .
\item[ 3 ] Computes general {\tt morpho\_lines} with 
{\em minvalue}=$v_i$ and {\em maxvalue}=$v_{i+1}$.
\item[ 4 ] Computes (more) general {\tt morpho\_lines} with 
{\em minvalue}=$v_{2i}$ and {\em maxvalue}=$v_{2i+1}$.
\end{itemize}
Where $i$ goes from 0 to $N$ for {\em ml\_opt} equal to 0, 1 or 2, 
thus obtaining $N+1$ slices.\\
For {\em ml\_opt}=3, $i$ will range from 0 to $N-1$, yielding $n$ slices. \\
Finally, for {\em ml\_opt}=4, there has to be an even number of values 
(i.e. $N+1$ even) and $i$ will range from 0 to $(N-1)/2$. This choice 
yields  $(N-1)/2$ different slices.

\bigskip

Exactly one option out of {\bf -L} and {\bf -l} has to be chosen.\\
For {\bf -L} only {\em ml\_opt} 0, 1 and 2 are available. \\
For {\em ml\_opt}=3
one must have {\em levels-$>$size}$\geq 2$\, , if {\em ml\_opt}=4 \,,
{\em levels-$>$size} has to be even. \\
Option {\bf -d} allows to obtain a b/w {\tt cimage} {\em c\_out}
of the {\tt morpho\_lines}. This option uses {\bf ml\_draw}. \\
{\em image\_in} is of format {\tt fimage} and {\em m\_image} of format
{\tt mimage}.\\
Notice that only {\em m\_image-$>$nrow}\, ,
{\em m\_image-$>$ncol}\, and {\em m\_image-$>$first\_ml} are set by the
module {\bf ml\_extract}.

The {\bf -m} flag allows to optimize memory occupation during
the decomposition. This is interesting if you use {\bf ml\_extract}
as UNIX command. Using this flag in an internal call
of the module {\bf ml\_extract()} and trying to delete
points separately in the sequel of your program will corrupt
the data structure.

\medskip

The {\tt morpho\_line} list {\em m\_image-$>$first\_ml} is ordered like
the data of {\em levels}, thus first  all the {\tt morpho\_lines}
associated to $v_0$ (and perhaps $v_1$) are listed, then those
associated to the next slice (see above how $i$ is incremented,
following the value of {\em ml\_opt}) until up to the 
last values of {\em levels-$>$values}.\\
Thus the order of the data in {\em levels} induces the order
of the slices (e.g. the {\tt morpho\_lines}) in {\em m\_image}. 
This is of importance if the {\tt mimage} is to be reconstructed
(see {\bf ml\_decompose} and {\bf ml\_reconstruct}).\\
Notice that we consider only 4-neighbourhood adjacancies to determine
which pixels are inside the set.

%--------------------------
\begin{figure*}[ht]
  \begin{center}
  \begin{picture}(170,160)(-2,-2)
  \thicklines
     \multiput(0,0)(0,30){5}{\multiput(-8,-8)(30,0){6}{\framebox(16,16)}}
     \put(-15,105){\circle*{4}}
     \multiput(15,15)(0,30){4}{\circle*{4}}
     \multiput(75,15)(0,30){4}{\circle*{4}} 
     \multiput(105,15)(30,0){2}{\multiput(0,0)(0,30){5}{\circle*{4}}} 
     \multiput(45,15)(0,90){2}{\circle*{4}}
     \put(45,135){\circle*{4}}
     \multiput(-27,0)(0,30){5}{\line(1,0){7}}
     \multiput(0,145)(30,0){6}{\line(0,-1){7}}
  \thinlines
    \multiput(-8,112)(30,0){2}{
       \put(0,0){\line(1,1){16}}
       \multiput(0,4)(4,-4){2}{\line(1,1){12}}
       \put(0,16){\line(1,-1){16}}
       \multiput(0,12)(4,4){2}{\line(1,-1){12}}
    }
    \multiput(0,0)(30,0){2}{
        \multiput(22,22)(0,30){3}{
           \put(0,0){\line(1,1){16}}
           \multiput(0,4)(4,-4){2}{\line(1,1){12}}
           \put(0,16){\line(1,-1){16}}
           \multiput(0,12)(4,4){2}{\line(1,-1){12}}
        } 
   }
   \multiput(112,22)(0,30){4}{
        \put(0,0){\line(1,1){16}}
        \multiput(0,4)(4,-4){2}{\line(1,1){12}}
        \put(0,16){\line(1,-1){16}}
        \multiput(0,12)(4,4){2}{\line(1,-1){12}}
   }
   \multiput(82,22)(0,60){2}{
        \put(0,0){\line(1,1){16}}
        \multiput(0,4)(4,-4){2}{\line(1,1){12}}
        \put(0,16){\line(1,-1){16}}
        \multiput(0,12)(4,4){2}{\line(1,-1){12}}
   }
     \multiput(25,15)(30,0){4}{\line(1,0){10}}
     \multiput(15,25)(120,0){2}{\multiput(0,0)(0,30){3}{\line(0,1){10}}}
     \multiput(85,45)(0,30){2}{\line(1,0){10}}
     \multiput(75,55)(30,0){2}{\line(0,1){10}}
     \put(-5,105){\line(1,0){10}}
     \multiput(55,105)(30,0){2}{\line(1,0){10}}
     \put(45,115){\line(0,1){10}} 
     \multiput(105,115)(30,0){2}{\line(0,1){10}} 
     \put(-4,105){\vector(1,0){6}}
     \put(94,105){\vector(-1,0){6}}
     \put(86,15){\vector(1,0){6}}
     \put(94,45){\vector(-1,0){6}}
     \put(135,117){\vector(0,1){6}}
     \multiput(-38,120)(38,36){2}{\makebox(0,0){\tiny 0}}
     \multiput(-38,90)(68,66){2}{\makebox(0,0){\tiny 1}}
     \put(-40,0){\makebox(0,0){\tiny $NL-1$}}
     \put(150,156){\makebox(0,0){\tiny $NC-1$}}
 \end{picture}
  \end{center}
  \label{fig_point_coord}
\end{figure*}
%----------------

\medskip

For each {\tt morpho\_line} the {\bf ml\_extract} module will set
a {\em minvalue} and a {\em maxvalue}, an open curve flag, 
a list of integer point coordinates and a list 
of the corresponding point types.

\smallskip

Notice that in a {\tt morpho\_line} a point never appears twice, 
thus for a closed line the first point and last point 
in the list are different.

\smallskip

In a {\tt morpho\_line} the points are listed such that 
the set is always left of the line. 

\smallskip

Be aware that {\bf ml\_extract} might create a very (!) large
data structure, depending on $N$ and  $NC*NL$.

\bigskip

Let us now give more details about the point coordinates of a
{\tt morpho\_line}. The figure\ref{fig_point_coord} below
 can be taken as illustration.
We have represented a {\tt morpho\_set} $MS$ with dashed squares
in an $5\times 6$ image (a pixel=a square), 
notice that in this example $MS$ is connected
(but not $MS^c$).

\medskip

The boundary between pixels is given by the list of their vertices,
drawn as black dots. The pixel coordinates being integer, $(i,j)$, the
vertices will have float coordinates $(i\pm 0.5 , j\pm 0.5)$\,,
but as {\tt morpho\_lines} are supposed to have integer coordinates
we will adopt the following\,: each vertex will be represented
by the integer coordinates obtained through a $(+0.5,+0.5)$
translation (see {\bf ml\_fml} and {\bf fml\_ml}).

\smallskip

Thus let $(k,l)$ be the coordinates  of a {\tt morpho\_line} point,
then the vertex it represents has float coordinates 
$(k-0.5 , l-0.5)$, where $k\in\{0,\ldots,NC\}$ and 
$l\in\{0,\ldots,NL\}$\,.

\smallskip

In the example the pixel $(3,2)\not\in MS$, has a boundary
defined by the float vertices $(2.5,1.5)$, $(3.5,1.5)$, 
$(3.5,2.5)$ and $(2.5,2.5)$. This {\tt morpho\_line}
will be saved as $(3,2)$, $(4,2)$, $(4,3)$ and $(3,3)$.
An open {\tt morpho\_line} starts/stops at points
having one coordinate either equal to 0, to $NC$ or to $NL$.

\medskip
These conventions are very important, they allow the
{\bf ml\_reconstruct} module to work correctly.

\medskip
Notice that a morpho\_line might be sometimes self-intersecting!\\
 Indeed look at the following ``picture'' $g$\,: 
\begin{tabular}{|c|c|c|}  \hline
0 & 0 & 0 \\ \hline
0 & 1 & 0 \\ \hline
1 & 0 & 0 \\ \hline
\end{tabular}

If we look for the sets $\{(i,j) \;/\; 1\leq g(i,j) \}$, we will
find two 4-connected sets (the two 1 pixels), 
there remains one region which is actually 8-connected. 
Now if we look for $\{(i,j) \;/\; g(i,j)\leq 0 \}$,
there is only one 4-connected set, having one boundary which
self-intersects ! \\
Thus if your application needs true Jordan curves
you should shrink the morpho\_lines around the morpho\_set.