
\paragraph{Mathematical description} \mbox{}

Given a shape which is define as a level set,
we compute the skeleton of this shape.
The underlying partial differential equation for this
algorithm is:
$$ \frac{\partial u}{\partial t} = |Du| (1+curv(u)).X_a$$
where $X_a$ is the stopping test based on the computation
of the width of the shape at the point x. If the width is too small,
the algorithm is stopped at the point x.

\paragraph{Options } \mbox{}

The option \verb+-n iteration+ fix the number of iterations to be done. 

The option \verb+-c Niter+ fix the number of iterations of the 
mean curvature motion. 

The option \verb+-l larg_min+ fix the minimal width for the skeleton.

The option \verb+-r radius+ fix the radius for the erosion.

The option \verb+-a+ changes the way the mean curvature motion is
computed: by default, the inf-sup filtering is iterated and 
with the option set, it is the following filtering:
(inf-sup + sup-inf)/2.

\paragraph{Inputs} \mbox{}

This module needs the name of a original image : {\it image}, and the
name of a Cmovie which corresponds to the set of the masks :$\cal B$. 
You can use any set of masks made, for example, using the module 
\verb+rotaffin+.
However, we advice you to use the standard set of masks called 
\verb+seg_mask+ (a plain segment).

\paragraph{Output} \mbox{}

This module generates in output a Cmovie where the successive skeletons 
are recorded.


\paragraph{References} \mbox{}

This program is associated to the article :

D. Pasquignon {\em Computation of a skeleton by partial differential
equation}
ICIP 1995.

See also :

F. Catte, F. Dibos. {\em A morphological approach of mean curvature motion.}, Report 9310, Ceremade, Univ. Paris-Dauphine 1993.

F. Catte, F. Dibos, G. Koepfler. {\em A morphological scheme for mean curvature motion and applications to anisotropic diffusion and motion of level sets.}, Report 9338, Ceremade, Univ. Paris-Dauphine 1993.

F. Catte, {\em Convergence of iterated affine and morphological filters by nonlinear semi-group theory} Preprint No 9528 CEREMADE 1995.

F. Guichard, {\em Axiomatisation des analyses multi-echelles d'images et de films.} PhD. Universite Paris IX, 1994.














