This user's macro allows to easily run a wavelet-denoising algorithm combining a total 
variation (TV) minimization approach. The first presentation of these method has been
made in~\cite{DF:ArtifactFree}, while in~\cite{DF:ReconsWaveletUsingTV} one
will find the detail of the algorithm together with the proof of the convergence.

In short, the approach is motivated by wavelet signal denoising methods, where 
thresholding small wavelet coefficients leads to pseudo-Gibbs artifacts. By replacing
these thresholded coefficients by values minimizing the total variation of the
reconstructed signal, the method performs a nearly artifact free signal denoising.

The meaning of options given in the usage are the following :

\begin{tabular}{lcl}
-P &:& give the percent of wavelet coefficients to remove.\\
-T &:& give the threshold.\\
-D &:& compute the threshold from the noise standard deviation (Donoho's threshold).\\
-O &:& give the wavelet filter.\\
-E &:& special edge processing (default is periodized).\\
-s &:& soft thresholding (default is hard thresholding).\\
-J &:& number of levels in the wavelet transform.\\
-N &:& number of iterations of the TV minimization algorithm.\\
-a &:& without -a compute exact TV, with -a a smooth version.\\
-I &:& allows to resume the TV minimization with previously denoised signal.\\
-S &:& output the reconstructed signal after wavelet thresholding.\\
-V &:& allows to output the signal having the minimal TV.\\
-r &:& relax constraint on approximation space V\_J.
\end{tabular}

From this list, the options you may want to set to get results close to the ones
reported in~\cite{DF:ArtifactFree} and~\cite{DF:ReconsWaveletUsingTV} are
{\tt -r}, {\tt -P} and {\tt -N}.

\begin{thebibliography}{Dau1}

\bibitem{DF:ArtifactFree}
S.~Durand and J.~Froment.
\newblock Artifact free signal denoising with wavelets.
\newblock In {\em Proc. of ICASSP'01}, volume~6, 2001.

\bibitem{DF:ReconsWaveletUsingTV}
Sylvain Durand and Jacques Froment.
\newblock Reconstruction of wavelet coefficients using total variation minimization.
\newblock {\em SIAM J. Sci. Comput.}, to appear. You can get the preprint number 2001-18
in the CMLA report pages {\tt www.cmla.ens-cachan.fr/Cmla/Publications/2001}.


\end{thebibliography}
